Well-quasi-orderings on word languages

### 2024-08-20 src/infixes.tex
tests and all
better figures

@@

>>>>

\begin{figure}
    \centering
    \includestandalone[width=\linewidth]{fig/infix-encoding-standalone}
    \caption{Representation of the \kl{subword relation} for $\set{a,b}^*$
        inside the \kl{infix relation} for $\set{a,b,c}^*$
        using the encoding of \cref{infix-embedding:thm}, restricted to words
        of length at most $3$.}
    \label{infix-embedding:fig}
\end{figure}

@@

\begin{figure}
    \centering
    TODO
    \caption{The gap words of an embedding between two 
    finite words}
    \label{gap-word-embedding:fig}
\end{figure}

\begin{figure}
    \centering
    TODO.
    \caption{Amalgamation of two runs on a picture}
    \label{amalgamation-runs:fig}
\end{figure}

### 2024-08-20 src/introduction.tex
better figures

\begin{figure}
    \centering
    \includestandalone{src/prefix-embedding-standalone}

    \includestandalone{src/infix-embedding-standalone}

    \includestandalone{src/subword-embedding-standalone}
    \caption{A simple representation of the \kl{subword relation},
        \kl{prefix relation},
        and \kl{infix relation},
        on the alphabet $\set{a,b}$ for words of
        length at most $3$.}
    \label{word-embeddings:fig}
\end{figure}

>>>>

\begin{figure}
    \centering
    \begin{tabular}{p{3cm}p{8cm}}
    Prefix Relation
    &
    \includestandalone[width=\linewidth]{fig/prefix-embedding-standalone}
    \\
    Infix relation
    &
    \includestandalone[width=\linewidth]{fig/infix-embedding-standalone}
    \\
    Subword relation
    &
    \includestandalone[width=\linewidth]{fig/subword-embedding-standalone}
    \end{tabular}
    \caption{A simple representation of the \kl{subword relation},
        \kl{prefix relation},
        and \kl{infix relation},
        on the alphabet $\set{a,b}$ for words of
        length at most $3$. The figures are Hasse Diagrams,
        representing the successor relation of the order.
        Furthermore, we highlight in red relations that are added
        when moving from the prefix relation to the infix one,
        and to the infix relation to the subword one.}
    \label{word-embeddings:fig}
\end{figure}
